Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2024-08-11 Thesis/03-chap3.qmd
try to fix alignment issue with chap 3

```{=html}
<table>
 <thead>
  <tr>
   <th style="text-align:left;"> <span data-qmd="Degree of Model Violations"></span> </th>
   <th style="text-align:center;"><span data-qmd="Range ($C$ = 10)"></span>  </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> <span data-qmd="Strong"></span>  </td>
   <td style="text-align:center;"> <span data-qmd="$\text{MVI} > 8$"></span>  </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="Moderate"></span>  </td>
   <td style="text-align:center;"> <span data-qmd="$6 < \text{MVI} < 8$"></span> </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="Weak"></span>  </td>
   <td style="text-align:center;"> <span data-qmd="$\text{MVI} < 6$"></span>  </td>
  </tr>
</tbody>
</table>

@@

```{r}
#| tbl-cap: "Degree of model violations or the strength of the visual signals according to the Model Violations Index (MVI). The constant $C$ is set to be 10."
#| label: tbl-mvi
data.frame(degree = c("Strong", "Moderate", "Weak"),
           range = c("$\\text{MVI} > 8$", "$6 < \\text{MVI} < 8$", "$\\text{MVI} < 6$")) %>%
  kableExtra::kable(booktabs = TRUE,
                    escape = FALSE,
                    col.names = c("Degree of model violations", "Range ($C$ = 10)"),
                    align = "lc")
```

@@

```{=html}
<table>
 <thead>
  <tr>
   <th style="text-align:left;"> Factor </th>
   <th style="text-align:left;"> Domain </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> j </td>
   <td style="text-align:left;"> {2, 3, ..., 18} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> a </td>
   <td style="text-align:left;"> [-1, 1] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> b </td>
   <td style="text-align:left;"> [0, 100] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\beta_1$"></span> </td>
   <td style="text-align:left;"> {0, 1} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\beta_2$"></span> </td>
   <td style="text-align:left;"> {0, 1} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\text{dist}_{\varepsilon}$"></span> </td>
   <td style="text-align:left;"> {discrete, uniform, normal, lognormal} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\text{dist}_{x1}$"></span> </td>
   <td style="text-align:left;"> {discrete, uniform, normal, lognormal} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\text{dist}_{x2}$"></span> </td>
   <td style="text-align:left;"> {discrete, uniform, normal, lognormal} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\sigma_{\varepsilon}$"></span> </td>
   <td style="text-align:left;"> [0.0625, 9] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\sigma_{X1}$"></span> </td>
   <td style="text-align:left;"> [0.3, 0.6] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\sigma_{X2}$"></span> </td>
   <td style="text-align:left;"> [0.3, 0.6] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> n </td>
   <td style="text-align:left;"> [50, 500] </td>
  </tr>
</tbody>
</table>

@@

```{r}
#| label: tbl-factor
#| tbl-cap: "Factors used in the data generating process for synthetic data simulation. Factor $j$ and $a$ controls the non-linearity shape and the heteroskedasticity shape respectively. Factor $b$, $\\sigma_\\varepsilon$ and $n$ control the signal strength. Factor $\\text{dist}_\\varepsilon$, $\\text{dist}_{x1}$ and $\\text{dist}_{x2}$ specifies the distribution of $\\varepsilon$, $X_1$ and $X_2$ respectively."
tibble(Factor = c("j", "a", "b", "$\\beta_1$", "$\\beta_2$", " $\\text{dist}_\\varepsilon$", "$\\text{dist}_{x1}$", "$\\text{dist}_{x2}$", "$\\sigma_{\\varepsilon}$", "$\\sigma_{X1}$", "$\\sigma_{X2}$", "n"),
       Domain = c("\\{2, 3, ..., 18\\}", "[-1, 1]", "[0, 100]", "\\{0, 1\\}", "\\{0, 1\\}", "\\{discrete, uniform, normal, lognormal\\}", "\\{discrete, uniform, normal, lognormal\\}", "\\{discrete, uniform, normal, lognormal\\}", "[0.0625, 9]", "[0.3, 0.6]", "[0.3, 0.6]", "[50, 500]")) %>%
  kableExtra::kable(escape = FALSE,
                    booktabs = TRUE)
```

@@

`````{=html}
<table>
 <thead>
  <tr>
   <th style="text-align:left;"> Hyperparameter </th>
   <th style="text-align:left;"> Domain </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> Number of base filters </td>
   <td style="text-align:left;"> {4, 8, 16, 32, 64} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Dropout rate for convolutional blocks </td>
   <td style="text-align:left;"> [0.1, 0.6] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Batch normalization for convolutional blocks </td>
   <td style="text-align:left;"> {false, true} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Type of global pooling </td>
   <td style="text-align:left;"> {max, average} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Ignore additional inputs </td>
   <td style="text-align:left;"> {false, true} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Number of units for the fully-connected layer </td>
   <td style="text-align:left;"> {128, 256, 512, 1024, 2048} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Batch normalization for the fully-connected layer </td>
   <td style="text-align:left;"> {false, true} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Dropout rate for the fully-connected layer </td>
   <td style="text-align:left;"> [0.1, 0.6] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Learning rate </td>
   <td style="text-align:left;"><span data-qmd = "[$10^{-8}$, $10^{-1}$]"></span> </td>
  </tr>
</tbody>
</table>

@@

```{r}
#| label: tbl-hyperparameter
#| tbl-cap: "Name of hyperparameters and their correspoding domain for the computer vision model."
data.frame(`Hyperparameter` = c("Number of base filters", "Dropout rate for convolutional blocks", "Batch normalization for convolutional blocks", "Type of global pooling", "Ignore additional inputs", "Number of units for the fully-connected layer", "Batch normalization for the fully-connected layer", "Dropout rate for the fully-connected layer", "Learning rate"),
           Domain = c("{4, 8, 16, 32, 64}", "[0.1, 0.6]", "{false, true}", "{max, average}", "{false, true}", "{128, 256, 512, 1024, 2048}", "{false, true}", "[0.1, 0.6]", "[$10^{-8}$, $10^{-1}$]")) %>%
  kableExtra::kable(booktabs = TRUE, escape = FALSE)
```

@@

`````{=html}
<table class="table" style="margin-left: auto; margin-right: auto;">
 <thead>
  <tr>
   <th style="text-align:left;"> Hyperparameter </th>
   <th style="text-align:left;"> <span data-qmd="$32 \times 32$"> </span> </th>
   <th style="text-align:left;"> <span data-qmd="$64 \times 64$"> </span> </th>
   <th style="text-align:left;"> <span data-qmd="$128 \times 128$"> </span> </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> Number of base filters </td>
   <td style="text-align:left;"> 32 </td>
   <td style="text-align:left;"> 64 </td>
   <td style="text-align:left;"> 64 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Dropout rate for convolutional blocks </td>
   <td style="text-align:left;"> 0.4 </td>
   <td style="text-align:left;"> 0.3 </td>
   <td style="text-align:left;"> 0.4 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Batch normalization for convolutional blocks </td>
   <td style="text-align:left;"> true </td>
   <td style="text-align:left;"> true </td>
   <td style="text-align:left;"> true </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Type of global pooling </td>
   <td style="text-align:left;"> max </td>
   <td style="text-align:left;"> average </td>
   <td style="text-align:left;"> average </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Ignore additional inputs </td>
   <td style="text-align:left;"> false </td>
   <td style="text-align:left;"> false </td>
   <td style="text-align:left;"> false </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Number of units for the fully-connected layer </td>
   <td style="text-align:left;"> 256 </td>
   <td style="text-align:left;"> 256 </td>
   <td style="text-align:left;"> 256 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Batch normalization for the fully-connected layer </td>
   <td style="text-align:left;"> false </td>
   <td style="text-align:left;"> true </td>
   <td style="text-align:left;"> true </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Dropout rate for the fully-connected layer </td>
   <td style="text-align:left;"> 0.2 </td>
   <td style="text-align:left;"> 0.4 </td>
   <td style="text-align:left;"> 0.1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Learning rate </td>
   <td style="text-align:left;"> 0.0003 </td>
   <td style="text-align:left;"> 0.0006 </td>
   <td style="text-align:left;"> 0.0052 </td>
  </tr>
</tbody>
</table>

@@

```{r}
#| label: tbl-best-hyperparameter
#| tbl-cap: "Hyperparameters values for the optimized computer vision models with different input sizes."
data.frame(`Hyperparameter` = c("Number of base filters", "Dropout rate for convolutional blocks", "Batch normalization for convolutional blocks", "Type of global pooling", "Ignore additional inputs", "Number of units for the fully-connected layer", "Batch normalization for the fully-connected layer", "Dropout rate for the fully-connected layer", "Learning rate"),
           `32` = c("32", "0.4", "true", "max", "false", "256", "false", "0.2", "0.0003"),
           `64` = c("64", "0.3", "true", "average", "false", "256", "true", "0.4", "0.0006"),
           `128` = c("64", "0.4", "true", "average", "false", "256", "true", "0.1", "0.0052")) %>%
  kableExtra::kable(booktabs = TRUE, 
                    col.names = c("Hyperparameter", "$32 \\times 32$", "$64 \\times 64$", "$128 \\times 128$"),
                    escape = FALSE) %>%
  kableExtra::kable_styling(latex_options = c("scale_down"))
```

@@

```{r}
#| label: tbl-performance
#| tbl-cap: "The test performance of three optimized models with different input sizes."
test_summary %>%
  select(res, RMSE, R2, MAE, HUBER) %>%
  mutate(res = glue::glue("${res} \\times {res}$")) %>%
  mutate(across(RMSE:MAE, ~format(.x, digits = 3))) %>%
  mutate(across(HUBER, ~format(.x, digits = 2))) %>%
  kableExtra::kable(booktabs = TRUE, 
                    escape = FALSE,
                    col.names = c("", "RMSE", "$R^2$", "MAE", "Huber loss"))
```

@@

```{=html}
<table>
 <thead>
  <tr>
   <th style="text-align:left;">  </th>
   <th style="text-align:left;"> RMSE </th>
   <th style="text-align:left;"> <span data-qmd="$R^2$"></span> </th>
   <th style="text-align:left;"> MAE </th>
   <th style="text-align:left;"> Huber loss </th>
  </tr>
 </thead>
<tbody>
<tr>
   <td style="text-align:left;padding-left: 2em;" indentlevel="1"> <span data-qmd="$32 \times 32$"></span> </td>
   <td style="text-align:left;"> 0.660 </td>
   <td style="text-align:left;"> 0.901 </td>
   <td style="text-align:left;"> 0.434 </td>
   <td style="text-align:left;"> 0.181 </td>
  </tr>
  <tr>
   <td style="text-align:left;padding-left: 2em;" indentlevel="1"> <span data-qmd="$64 \times 64$"></span> </td>
   <td style="text-align:left;"> 0.674 </td>
   <td style="text-align:left;"> 0.897 </td>
   <td style="text-align:left;"> 0.438 </td>
   <td style="text-align:left;"> 0.186 </td>
  </tr>
  <tr>
   <td style="text-align:left;padding-left: 2em;" indentlevel="1"> <span data-qmd="$128 \times 128$"></span> </td>
   <td style="text-align:left;"> 0.692 </td>
   <td style="text-align:left;"> 0.892 </td>
   <td style="text-align:left;"> 0.460 </td>
   <td style="text-align:left;"> 0.199 </td>
  </tr>
</tbody>
</table>

@@

```{=html}
<table class="table" style="margin-left: auto; margin-right: auto;">
 <thead>
  <tr>
   <th style="text-align:left;"> Violations </th>
   <th style="text-align:left;"> #samples </th>
   <th style="text-align:left;"> RMSE </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> no violations </td>
   <td style="text-align:left;"> 155 </td>
   <td style="text-align:left;"> 1.267 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> non-linearity </td>
   <td style="text-align:left;"> 2218 </td>
   <td style="text-align:left;"> 0.787 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> heteroskedasticity </td>
   <td style="text-align:left;"> 1067 </td>
   <td style="text-align:left;"> 0.602 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> non-linearity + heteroskedasticity </td>
   <td style="text-align:left;"> 985 </td>
   <td style="text-align:left;"> 0.751 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> non-normality </td>
   <td style="text-align:left;"> 1111 </td>
   <td style="text-align:left;"> 0.320 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> non-linearity + non-normality </td>
   <td style="text-align:left;"> 928 </td>
   <td style="text-align:left;"> 0.600 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> heteroskedasticity + non-normality </td>
   <td style="text-align:left;"> 819 </td>
   <td style="text-align:left;"> 0.489 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> non-linearity + heteroskedasticity + non-normality </td>
   <td style="text-align:left;"> 717 </td>
   <td style="text-align:left;"> 0.620 </td>
  </tr>
</tbody>
</table>

@@

```{r}
#| label: tbl-performance-sub
#| tbl-cap: "The training and test performance of the $32 \\times 32$ model presented with different model violations."
model_pred %>%
  filter(res == 32L) %>%
  group_by(include_non_normal, include_heter, include_z) %>%
  summarise(train_n = sum(type == "train"),
            train_RMSE = yardstick::rmse_vec(effect_size[type == "train"], vss[type == "train"]),
            test_n = sum(type == "test"),
            test_RMSE = yardstick::rmse_vec(effect_size[type == "test"], vss[type == "test"])) %>%
  mutate(violations = ifelse(include_z, "non-linearity", "null")) %>%
  mutate(violations = ifelse(include_heter, glue("{violations} + heteroskedasticity"), violations)) %>%
  mutate(violations = ifelse(include_non_normal, glue("{violations} + non-normality"), violations)) %>%
  mutate(violations = gsub("null \\+ ", "", violations)) %>%
  ungroup() %>%
  select(violations, train_n, train_RMSE, test_n, test_RMSE) %>%
  mutate(train_n = format(train_n)) %>%
  mutate(test_n = format(test_n)) %>%
  mutate(across(c(train_RMSE, test_RMSE), ~format(.x, digits = 3))) %>%
  mutate(violations = ifelse(violations == "null", "no violations", violations)) %>%
  select(-train_n, -train_RMSE) %>%
  kableExtra::kable(booktabs = TRUE,
                    escape = FALSE,
                    linesep = "", 
                    col.names = c("Violations", "\\#samples", "RMSE")) %>%
  kableExtra::kable_styling(latex_options = c("scale_down"))
```

>>>>

```{=html}
<table>
 <thead>
  <tr>
   <th style="text-align:center;"> <span data-qmd="Degree of Model Violations"></span> </th>
   <th style="text-align:center;"><span data-qmd="Range ($C$ = 10)"></span>  </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> <span data-qmd="Strong"></span>  </td>
   <td style="text-align:center;"> <span data-qmd="$\text{MVI} > 8$"></span>  </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="Moderate"></span>  </td>
   <td style="text-align:center;"> <span data-qmd="$6 < \text{MVI} < 8$"></span> </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="Weak"></span>  </td>
   <td style="text-align:center;"> <span data-qmd="$\text{MVI} < 6$"></span>  </td>
  </tr>
</tbody>
</table>

@@

```{r}
#| tbl-cap: "Degree of model violations or the strength of the visual signals according to the Model Violations Index (MVI). The constant $C$ is set to be 10."
#| label: tbl-mvi
data.frame(degree = c("Strong", "Moderate", "Weak"),
           range = c("$\\text{MVI} > 8$", "$6 < \\text{MVI} < 8$", "$\\text{MVI} < 6$")) %>%
  kableExtra::kable(booktabs = TRUE,
                    escape = FALSE,
                    col.names = c("Degree of model violations", "Range ($C$ = 10)"),
                    align = "lc") %>%
  kableExtra::row_spec(0, align = "c")
```

@@

```{=html}
<table>
 <thead>
  <tr>
   <th style="text-align:center;"> Factor </th>
   <th style="text-align:center;"> Domain </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> j </td>
   <td style="text-align:left;"> {2, 3, ..., 18} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> a </td>
   <td style="text-align:left;"> [-1, 1] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> b </td>
   <td style="text-align:left;"> [0, 100] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\beta_1$"></span> </td>
   <td style="text-align:left;"> {0, 1} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\beta_2$"></span> </td>
   <td style="text-align:left;"> {0, 1} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\text{dist}_{\varepsilon}$"></span> </td>
   <td style="text-align:left;"> {discrete, uniform, normal, lognormal} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\text{dist}_{x1}$"></span> </td>
   <td style="text-align:left;"> {discrete, uniform, normal, lognormal} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\text{dist}_{x2}$"></span> </td>
   <td style="text-align:left;"> {discrete, uniform, normal, lognormal} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\sigma_{\varepsilon}$"></span> </td>
   <td style="text-align:left;"> [0.0625, 9] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\sigma_{X1}$"></span> </td>
   <td style="text-align:left;"> [0.3, 0.6] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> <span data-qmd="$\sigma_{X2}$"></span> </td>
   <td style="text-align:left;"> [0.3, 0.6] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> n </td>
   <td style="text-align:left;"> [50, 500] </td>
  </tr>
</tbody>
</table>

@@

```{r}
#| label: tbl-factor
#| tbl-cap: "Factors used in the data generating process for synthetic data simulation. Factor $j$ and $a$ controls the non-linearity shape and the heteroskedasticity shape respectively. Factor $b$, $\\sigma_\\varepsilon$ and $n$ control the signal strength. Factor $\\text{dist}_\\varepsilon$, $\\text{dist}_{x1}$ and $\\text{dist}_{x2}$ specifies the distribution of $\\varepsilon$, $X_1$ and $X_2$ respectively."
tibble(Factor = c("j", "a", "b", "$\\beta_1$", "$\\beta_2$", " $\\text{dist}_\\varepsilon$", "$\\text{dist}_{x1}$", "$\\text{dist}_{x2}$", "$\\sigma_{\\varepsilon}$", "$\\sigma_{X1}$", "$\\sigma_{X2}$", "n"),
       Domain = c("\\{2, 3, ..., 18\\}", "[-1, 1]", "[0, 100]", "\\{0, 1\\}", "\\{0, 1\\}", "\\{discrete, uniform, normal, lognormal\\}", "\\{discrete, uniform, normal, lognormal\\}", "\\{discrete, uniform, normal, lognormal\\}", "[0.0625, 9]", "[0.3, 0.6]", "[0.3, 0.6]", "[50, 500]")) %>%
  kableExtra::kable(escape = FALSE,
                    booktabs = TRUE) %>%
  kableExtra::row_spec(0, align = "c")
```

@@

`````{=html}
<table>
 <thead>
  <tr>
   <th style="text-align:center;"> Hyperparameter </th>
   <th style="text-align:center;"> Domain </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> Number of base filters </td>
   <td style="text-align:left;"> {4, 8, 16, 32, 64} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Dropout rate for convolutional blocks </td>
   <td style="text-align:left;"> [0.1, 0.6] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Batch normalization for convolutional blocks </td>
   <td style="text-align:left;"> {false, true} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Type of global pooling </td>
   <td style="text-align:left;"> {max, average} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Ignore additional inputs </td>
   <td style="text-align:left;"> {false, true} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Number of units for the fully-connected layer </td>
   <td style="text-align:left;"> {128, 256, 512, 1024, 2048} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Batch normalization for the fully-connected layer </td>
   <td style="text-align:left;"> {false, true} </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Dropout rate for the fully-connected layer </td>
   <td style="text-align:left;"> [0.1, 0.6] </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Learning rate </td>
   <td style="text-align:left;"><span data-qmd = "[$10^{-8}$, $10^{-1}$]"></span> </td>
  </tr>
</tbody>
</table>

@@

```{r}
#| label: tbl-hyperparameter
#| tbl-cap: "Name of hyperparameters and their correspoding domain for the computer vision model."
data.frame(`Hyperparameter` = c("Number of base filters", "Dropout rate for convolutional blocks", "Batch normalization for convolutional blocks", "Type of global pooling", "Ignore additional inputs", "Number of units for the fully-connected layer", "Batch normalization for the fully-connected layer", "Dropout rate for the fully-connected layer", "Learning rate"),
           Domain = c("{4, 8, 16, 32, 64}", "[0.1, 0.6]", "{false, true}", "{max, average}", "{false, true}", "{128, 256, 512, 1024, 2048}", "{false, true}", "[0.1, 0.6]", "[$10^{-8}$, $10^{-1}$]")) %>%
  kableExtra::kable(booktabs = TRUE, escape = FALSE) %>%
  kableExtra::row_spec(0, align = "c")
```

@@

`````{=html}
<table class="table" style="margin-left: auto; margin-right: auto;">
 <thead>
  <tr>
   <th style="text-align:center;"> Hyperparameter </th>
   <th style="text-align:center;"> <span data-qmd="$32 \times 32$"> </span> </th>
   <th style="text-align:center;"> <span data-qmd="$64 \times 64$"> </span> </th>
   <th style="text-align:center;"> <span data-qmd="$128 \times 128$"> </span> </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> Number of base filters </td>
   <td style="text-align:left;"> 32 </td>
   <td style="text-align:left;"> 64 </td>
   <td style="text-align:left;"> 64 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Dropout rate for convolutional blocks </td>
   <td style="text-align:left;"> 0.4 </td>
   <td style="text-align:left;"> 0.3 </td>
   <td style="text-align:left;"> 0.4 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Batch normalization for convolutional blocks </td>
   <td style="text-align:left;"> true </td>
   <td style="text-align:left;"> true </td>
   <td style="text-align:left;"> true </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Type of global pooling </td>
   <td style="text-align:left;"> max </td>
   <td style="text-align:left;"> average </td>
   <td style="text-align:left;"> average </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Ignore additional inputs </td>
   <td style="text-align:left;"> false </td>
   <td style="text-align:left;"> false </td>
   <td style="text-align:left;"> false </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Number of units for the fully-connected layer </td>
   <td style="text-align:left;"> 256 </td>
   <td style="text-align:left;"> 256 </td>
   <td style="text-align:left;"> 256 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Batch normalization for the fully-connected layer </td>
   <td style="text-align:left;"> false </td>
   <td style="text-align:left;"> true </td>
   <td style="text-align:left;"> true </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Dropout rate for the fully-connected layer </td>
   <td style="text-align:left;"> 0.2 </td>
   <td style="text-align:left;"> 0.4 </td>
   <td style="text-align:left;"> 0.1 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> Learning rate </td>
   <td style="text-align:left;"> 0.0003 </td>
   <td style="text-align:left;"> 0.0006 </td>
   <td style="text-align:left;"> 0.0052 </td>
  </tr>
</tbody>
</table>

@@

```{r}
#| label: tbl-best-hyperparameter
#| tbl-cap: "Hyperparameters values for the optimized computer vision models with different input sizes."
data.frame(`Hyperparameter` = c("Number of base filters", "Dropout rate for convolutional blocks", "Batch normalization for convolutional blocks", "Type of global pooling", "Ignore additional inputs", "Number of units for the fully-connected layer", "Batch normalization for the fully-connected layer", "Dropout rate for the fully-connected layer", "Learning rate"),
           `32` = c("32", "0.4", "true", "max", "false", "256", "false", "0.2", "0.0003"),
           `64` = c("64", "0.3", "true", "average", "false", "256", "true", "0.4", "0.0006"),
           `128` = c("64", "0.4", "true", "average", "false", "256", "true", "0.1", "0.0052")) %>%
  kableExtra::kable(booktabs = TRUE, 
                    col.names = c("Hyperparameter", "$32 \\times 32$", "$64 \\times 64$", "$128 \\times 128$"),
                    escape = FALSE) %>%
  kableExtra::kable_styling(latex_options = c("scale_down")) %>%
  kableExtra::row_spec(0, align = "c")
```

@@

```{r}
#| label: tbl-performance
#| tbl-cap: "The test performance of three optimized models with different input sizes."
test_summary %>%
  select(res, RMSE, R2, MAE, HUBER) %>%
  mutate(res = glue::glue("${res} \\times {res}$")) %>%
  mutate(across(RMSE:MAE, ~format(.x, digits = 3))) %>%
  mutate(across(HUBER, ~format(.x, digits = 2))) %>%
  kableExtra::kable(booktabs = TRUE, 
                    escape = FALSE,
                    align = "lrrrr",
                    col.names = c("", "RMSE", "$R^2$", "MAE", "Huber loss")) %>%
  kableExtra::row_spec(0, align = "c")
```

@@

```{=html}
<table>
 <thead>
  <tr>
   <th style="text-align:center;">  </th>
   <th style="text-align:center;"> RMSE </th>
   <th style="text-align:center;"> <span data-qmd="$R^2$"></span> </th>
   <th style="text-align:center;"> MAE </th>
   <th style="text-align:center;"> Huber loss </th>
  </tr>
 </thead>
<tbody>
<tr>
   <td style="text-align:left;padding-left: 2em;" indentlevel="1"> <span data-qmd="$32 \times 32$"></span> </td>
   <td style="text-align:right;"> 0.660 </td>
   <td style="text-align:right;"> 0.901 </td>
   <td style="text-align:right;"> 0.434 </td>
   <td style="text-align:right;"> 0.181 </td>
  </tr>
  <tr>
   <td style="text-align:left;padding-left: 2em;" indentlevel="1"> <span data-qmd="$64 \times 64$"></span> </td>
   <td style="text-align:right;"> 0.674 </td>
   <td style="text-align:right;"> 0.897 </td>
   <td style="text-align:right;"> 0.438 </td>
   <td style="text-align:right;"> 0.186 </td>
  </tr>
  <tr>
   <td style="text-align:left;padding-left: 2em;" indentlevel="1"> <span data-qmd="$128 \times 128$"></span> </td>
   <td style="text-align:right;"> 0.692 </td>
   <td style="text-align:right;"> 0.892 </td>
   <td style="text-align:right;"> 0.460 </td>
   <td style="text-align:right;"> 0.199 </td>
  </tr>
</tbody>
</table>

@@

```{=html}
<table class="table" style="margin-left: auto; margin-right: auto;">
 <thead>
  <tr>
   <th style="text-align:center;"> Violations </th>
   <th style="text-align:center;"> #samples </th>
   <th style="text-align:center;"> RMSE </th>
  </tr>
 </thead>
<tbody>
  <tr>
   <td style="text-align:left;"> no violations </td>
   <td style="text-align:right;"> 155 </td>
   <td style="text-align:right;"> 1.267 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> non-linearity </td>
   <td style="text-align:right;"> 2218 </td>
   <td style="text-align:right;"> 0.787 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> heteroskedasticity </td>
   <td style="text-align:right;"> 1067 </td>
   <td style="text-align:right;"> 0.602 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> non-linearity + heteroskedasticity </td>
   <td style="text-align:right;"> 985 </td>
   <td style="text-align:right;"> 0.751 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> non-normality </td>
   <td style="text-align:right;"> 1111 </td>
   <td style="text-align:right;"> 0.320 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> non-linearity + non-normality </td>
   <td style="text-align:right;"> 928 </td>
   <td style="text-align:right;"> 0.600 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> heteroskedasticity + non-normality </td>
   <td style="text-align:right;"> 819 </td>
   <td style="text-align:right;"> 0.489 </td>
  </tr>
  <tr>
   <td style="text-align:left;"> non-linearity + heteroskedasticity + non-normality </td>
   <td style="text-align:right;"> 717 </td>
   <td style="text-align:right;"> 0.620 </td>
  </tr>
</tbody>
</table>

@@

```{r}
#| label: tbl-performance-sub
#| tbl-cap: "The training and test performance of the $32 \\times 32$ model presented with different model violations."
model_pred %>%
  filter(res == 32L) %>%
  group_by(include_non_normal, include_heter, include_z) %>%
  summarise(train_n = sum(type == "train"),
            train_RMSE = yardstick::rmse_vec(effect_size[type == "train"], vss[type == "train"]),
            test_n = sum(type == "test"),
            test_RMSE = yardstick::rmse_vec(effect_size[type == "test"], vss[type == "test"])) %>%
  mutate(violations = ifelse(include_z, "non-linearity", "null")) %>%
  mutate(violations = ifelse(include_heter, glue("{violations} + heteroskedasticity"), violations)) %>%
  mutate(violations = ifelse(include_non_normal, glue("{violations} + non-normality"), violations)) %>%
  mutate(violations = gsub("null \\+ ", "", violations)) %>%
  ungroup() %>%
  select(violations, train_n, train_RMSE, test_n, test_RMSE) %>%
  mutate(train_n = format(train_n)) %>%
  mutate(test_n = format(test_n)) %>%
  mutate(across(c(train_RMSE, test_RMSE), ~format(.x, digits = 3))) %>%
  mutate(violations = ifelse(violations == "null", "no violations", violations)) %>%
  select(-train_n, -train_RMSE) %>%
  kableExtra::kable(booktabs = TRUE,
                    escape = FALSE,
                    linesep = "", 
                    align = "lrr",
                    col.names = c("Violations", "\\#samples", "RMSE")) %>%
  kableExtra::kable_styling(latex_options = c("scale_down")) %>%
  kableExtra::row_spec(0, align = "c")
```
